---
title: "Dated Thallatosuchian phylogenetics using MrBayes"
output: 
  pdf_document:
    latex_engine: xelatex
toc: true
urlcolor: blue
mainfont: Calibri
fontsize: 12
---

```{r setup, include=FALSE}
require(knitr)
knitr::opts_chunk$set(echo = FALSE,
                      warning=FALSE,
                      message=FALSE,
                      dev = 'pdf',
                      fig.align='center')
```

#Outline
The purpose of this Rmarkdown document is to allow users to follow our plotting methods for the dated Bayesian analyses. Analyses are performed using separate R scripts called by this document and users should refer to the unrendered [Croc_notebook.Rmd](https://github.com/James-Kitson/Dating_Crocs.git) file for links to the relevant scripts.
\newpage

#Analysis with Thallatosuchian root unconstrained
```{r echo=FALSE}
read_chunk('R_scripts/Croc_tree_plotting_unconstrained_Thallatosuchia.R')
```
```{r fig.width=7, fig.height=9.5, message=F, warning=F}
<<unconstrained_treeprocess>>
<<unconstrained_treeplot>>
##<<unconstrained_lttplot>>
```
\newpage
#Analysis with Thallatosuchian root constrained between 191 mya and 201 mya.

```{r echo=FALSE}
read_chunk('R_scripts/Croc_tree_plotting_constrained_201Ma_Thallatosuchia.R')
```
```{r fig.width=7, fig.height=9.5, message=F, warning=F}
<<constrained_201_treeprocess>>
<<constrained_201_treeplot>>
##<<constrained_lttplot>>
```
\newpage
#Analysis with Thallatosuchian root constrained between 205 mya and 215 mya.

```{r echo=FALSE}
read_chunk('R_scripts/Croc_tree_plotting_constrained_215Ma_Thallatosuchia.R')
```
```{r fig.width=7, fig.height=9.5, message=F, warning=F}
<<constrained_215_treeprocess>>
<<constrained_215_treeplot>>
##<<constrained_lttplot>>
```
\newpage
#Lineage through time comparison plots
```{r echo=FALSE}
read_chunk('R_scripts/ltt_comparison.R')
```
```{r fig.width=7, fig.height=7, message=F, warning=F}
<<lttcomparisonprocess>>
<<lttcomparisonplot>>
```

